The investment strategy based on behavior of artificial earthworm for use in algotrading

### 2014-05-05 Article/Article20140406Granada/LatexArt/article_main.tex
minipages

\usepackage{amssymb}
\setcounter{tocdepth}{3}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{amsmath}
\usepackage{placeins}

@@

\begin{figure}[h!]
\centering
\includegraphics[width = 0.6\textwidth]{figures/rys12.png}
\caption{Balance (relative value) in Matlab for GBPUSD [1h] in period 2013.01.09 - 2013.12.30 with fixed parameters p1-p5.}
\label{fig:fig12}
\end{figure}
\FloatBarrier
\begin{figure}[h!]
\centering
\includegraphics[width = 0.6\textwidth]{figures/rys13.png}
\caption{Balance (absolute value) in MetaTrader for GBPUSD [1h] in period 2013.01.09 - 2013.12.30 with fixed parameters p1-p5.}
\label{fig:fig13}
\end{figure}
\FloatBarrier

@@

\begin{figure}[h!]
\centering
\includegraphics[width = 0.6\textwidth]{figures/rys14.png}
\caption{Balance (relative value) in Matlab for GBPUSD [1h] in period 2013.01.09 - 2013.12.30 with dynamic p1-p5.}
\label{fig:fig14}
\end{figure}
\FloatBarrier
\begin{figure}[h!]
\centering
\includegraphics[width = 0.6\textwidth]{figures/rys15.png}
\caption{Balance (absolute value) in MetaTrader for GBPUSD [1h] in period 2013.01.09 - 2013.12.30 with dynamic p1-p5.}
\label{fig:fig15}
\end{figure}
\FloatBarrier

>>>>

\usepackage{amssymb}
\setcounter{tocdepth}{3}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{amsmath}
\usepackage{placeins}
\usepackage{subcaption}
\captionsetup{compatibility=false}

@@

\begin{figure}[h!]
\begin{minipage}{0.49\textwidth}
\centering
\includegraphics[width = 0.9\textwidth]{figures/rys12.png}
\subcaption{} % Balance (relative value) in Matlab for GBPUSD [1h] in period 2013.01.09 - 2013.12.30 with fixed parameters p1-p5.
\label{fig:fig12}
\end{minipage}
\begin{minipage}{0.49\textwidth}
\centering
\includegraphics[width = \textwidth]{figures/rys13.png}
\subcaption{} % Balance (absolute value) in MetaTrader for GBPUSD [1h] in period 2013.01.09 - 2013.12.30 with fixed parameters p1-p5.
\label{fig:fig13}
\end{minipage}
\caption{CAPTION GOES HERE}
\end{figure}
\FloatBarrier

@@

\begin{figure}[h!]
\begin{minipage}{0.49\textwidth}
\centering
\includegraphics[width = 0.9\textwidth]{figures/rys14.png}
\subcaption{} %Balance (relative value) in Matlab for GBPUSD [1h] in period 2013.01.09 - 2013.12.30 with dynamic p1-p5.
\label{fig:fig14}
\end{minipage}
\begin{minipage}{0.49\textwidth}
\centering
\includegraphics[width = \textwidth]{figures/rys15.png}
\subcaption{} %Balance (absolute value) in MetaTrader for GBPUSD [1h] in period 2013.01.09 - 2013.12.30 with dynamic p1-p5.
\label{fig:fig15}
\end{minipage}
\caption{CAPTION GOES HERE}
\end{figure}
\FloatBarrier
